\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-09-16 paperITSC.tex
Abstract test commit

With the increasing number of vehicles on road, traffic related problems like congestion, traffic jams, environmental pollution, and accidents, are very common these days. To solve transportation related problems and make the driving experience safer, comfortable and enjoyable, VANETs were developed. A large number of applications, ranges from safety to non-safety purposes, are envisioned for VANETs. These applications make use of opportunistic encounters to forward messages. However, the unique characteristics of VANETs, make the opportunistic forwarding a challenging task. In this paper we proposed a novel protocol called called Message Forwarding by Categorization of Vehicles (\emph{MFCV}). Our protocol exploits contextual information and vehicles categorization to improve opportunistic forwarding of messages. We validate and compare our protocol with the Epidemic routing protocol, by means of a series of simulation experiments. Our protocol performed very close to the Epidemic protocol, in terms of messages delivery. Additionally, our results showed improved performance when vehicles categorization was consider in the forwarding decision. Finally, (\emph{MFCV}) performed better in terms of message latency, and resource utilization.

>>>>

With the increasing number of vehicles on the roads, traffic related problems like congestion, traffic jams, environmental pollution, and accidents, are very common these days. To solve transportation-related problems and make the driving experience safer, comfortable and enjoyable, VANETs were developed. A large number of applications ranges from safety to non-safety purposes are envisioned for VANETs. These applications make use of opportunistic encounters to forward messages. However, the unique characteristics of VANETs, make the opportunistic forwarding a challenging task. In this paper, we proposed a novel protocol called Message Forwarding by Categorization of Vehicles (\emph{MFCV}). Our protocol exploits contextual information and vehicles categorization to improve opportunistic forwarding of messages. We validate and compare our protocol with the Epidemic routing protocol, by means of a series of simulation experiments. Our protocol performed very close to the Epidemic protocol, in terms of messages delivery. Additionally, our results showed improved performance when vehicles categorization was considered in the forwarding decision. Finally, (\emph{MFCV}) performed better in terms of message latency, and resource utilization.
